\racets: Faceted Execution in Racket

### 2018-07-24 paper/paper.tex
abstract draft

\title{\racets: Policy{-}Agnostic Programming in Racket}

@@

\begin{abstract}lorem ipsum...\end{abstract}

@@

>>>>

\title{\racets: Faceted Execution in Racket}

@@

@@

\begin{abstract}
  Faceted execution is a linguistic paradigm for dynamic information-flow
  control with the distinguishing feature that some program values may be
  \emph{faceted}. Faceted values simulate multiple executions (for different
  combinations of security labels) at once. This enables policy-agnostic programming:
  a style of programming where information-flow policies are stated independently
  of core program logic and are then enforced at runtime by a dynamic monitor. This
  approach enforces privacy constraints without requiring systems to be updated at every
  relevant code-point whenever a privacy policy needs to be added or changed.

  In this paper, we present \racets: an implementation of faceted execution for
  core language features such as application, mutation, and conditionals, using
  Racket's macro system. As Racket permits even core forms to be instrumented
  or rewritten arbitrarily, we are able to design a library of macros for 
  faceted execution in Scheme. We review faceted execution, formalize its operation,
  show how these big-step rules are turned into macros, and then discuss
  issues of interoperability with non-faceted Racket code.
\end{abstract}
